---
title: "housingPriceAna"
author: "Chengjia Wang"
date: "19 June 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# SVM Regression
Following the experiments in my Matlab code, we continue with the our regression model.
Because of the limit of time, I won't perform a complicated experiment as I did in Matlab.
Just a simple SVM regression (SVR) model and calculate the RMS error.
SVM regression: we have a wide choice of libs, e.g., e1701, randomForrest, stats, knn, the famous caret, etc.
Here we use e1701, one of the mostly used reg/clas lib
```{r}
library(e1071)
library(ggplot2)
```

## 1. load and clean data 

### Set Paths
```{r}
dataDir <- "/home/cwang/Desktop/amazonInterview/RCode/"
trStruc.name <- "trainFile.csv"
teStruc.name <- "testFile.csv"
```

### Read data
```{r}
trStruc.Data <- read.csv(paste(dataDir, trStruc.name, sep=""), header = FALSE)
teStruc.Data <- read.csv(paste(dataDir, teStruc.name, sep=""), header = FALSE)
```

### Clean data: sort data based on date, normalize date as number of days
```{r}
colnames(trStruc.Data) <- c("Price", "Date", "Type", "London", "Lease")
colnames(teStruc.Data) <- c("Price", "Date", "Type", "London", "Lease")
trStruc.Data <- trStruc.Data[order(trStruc.Data$Date), ]
teStruc.Data <- teStruc.Data[order(teStruc.Data$Date), ]
teStruc.Data$Date <- teStruc.Data$Date - min(trStruc.Data$Date)
trStruc.Data$Date <- trStruc.Data$Date - min(trStruc.Data$Date)
```

### Set feature and value
```{r}
trStruc.X = trStruc.Data[, 2:5]
trStruc.Y = trStruc.Data[, 1]
teStruc.X = teStruc.Data[ , 2:5]
teStruc.Y = teStruc.Data[, 1]
```

## 2. fit the model
```{r qplot, fig.width=4, fig.height=3, message=FALSE}
svStruc.model <- svm(trStruc.X, trStruc.Y)
svStruc.trY <- predict(svStruc.model, trStruc.X)
# plot
ggplot(cbind(trStruc.X, trStruc.Y), aes(x=Date, y=trStruc.Y) ) + geom_point() + geom_smooth()
```

### calculate the error
```{r}
svStruc.trErrors <- trStruc.Y-svStruc.trY
svStruc.trError <- sqrt(mean(svStruc.trErrors^2))
print (paste('Training RMS error is: ', svStruc.trError, sep = ""))
```

## 3. test the model
```{r}
svStruc.teY = predict(svStruc.model, teStruc.X)
svStruc.teErrors <- teStruc.Y-svStruc.teY
svStruc.teError <- sqrt(mean(svStruc.teErrors^2))
print (paste('Testing RMS error is: ', svStruc.teError, sep = ""))
```

Looks better than in Matlab

## 4. we can tune the model using R function tune(svm, ...)
